---
title: "tnum_615"
output: html_document
date: "2022-11-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Tnum set up

```{r}
library(tnum)
tnum.loadLibs() 
tnum.authorize(ip = "mssp.truenum.com:8080", creds = "yiryuan@bu.edu:leopard")
```

## Query Weena

```{r}

ch8_weena <- data.frame(tnum.query("subj:Time_Machine:Chapter:8:* and stringval:Weena"))
ch10_weena <- data.frame(tnum.query("subj:Time_Machine:Chapter:10:* and stringval:Weena"))
ch11_weena <- data.frame(tnum.query("subj:Time_Machine:Chapter:11:* and stringval:Weena"))
ch12_weena <- data.frame(tnum.query("subj:Time_Machine:Chapter:12:* and stringval:Weena"))
all_weena <- data.frame(tnum.query("subj:Time_Machine:* and stringval:Weena"))
```
## Plot Wenna


```{r}
weena<-rbind(ch8_weena,ch10_weena,ch11_weena,ch12_weena,all_weena)
tnum.graphTnumList(weena)
```
```{r}
library(dplyr)
library(tidytext) 
library(ggplot2)
text<-c(weena$value)
df <- tibble(text)

s1<-df %>%
  unnest_tokens(word, text)

s2 <- s1 %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

s2 %>%
  group_by(sentiment) %>%
  slice_max(n, n = 5) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)

```


## The word "Weena" shows in chapters 8 - 12. The Time Machine has 15 Chapters, so "Weena" appears in the later half of the book. "Weena" first appears in chapter 8 and we can know that "Weena" is a woman in chapter 8. "Weena" often shows in the later part, so she is an important character in the 8-12 chapters. The sentiment analysis displays the positive word "well" and the negative word "tired" always goes along with  "Weena".

##Query Psychologist
```{r}
ch1_Psy <- data.frame(tnum.query("subj:Time_Machine:Chapter:1:* and stringval:Psychologist"))
ch2_Psy <- data.frame(tnum.query("subj:Time_Machine:Chapter:2:* and stringval:Psychologist"))

```

##Plot Psy
```{r}
psy<-rbind(ch1_Psy,ch2_Psy)
tnum.graphTnumList(psy)
```
## The word "Psychologist" only appears in Chapters 1 & 2. The "Psychologist" 5 times in Chapter 1 and 11 times in Chapter "Psychologist" appears more times in Chapter 2 than in Chapter 1. The "Psychologist" plays a vital role at the beginning of The Time Machine. By querying the values which contain the word "Psychologist", we can find psychologist test the existence of time traveler. 


##Query Terror
```{r}
ch7_terror <- data.frame(tnum.query("subj:Time_Machine:Chapter:7:* and stringval:terror"))
ch8_terror <- data.frame(tnum.query("subj:Time_Machine:Chapter:8:* and stringval:terror"))
ch9_terror <- data.frame(tnum.query("subj:Time_Machine:Chapter:9:* and stringval:terror"))
ch10_terror <- data.frame(tnum.query("subj:Time_Machine:Chapter:10:* and stringval:terror"))
all_terror <- data.frame(tnum.query("subj:Time_Machine:* and stringval:terror"))

```

```{r}
terror<-rbind(ch7_terror,ch8_terror,ch9_terror,ch10_terror,all_terror)
tnum.graphTnumList(terror)
```
##The "word" terror shows in chapters 7-10, 13 and it only appears one or two times in these chapters. Obviously, the word "terror" is low frequency word in The Time Machine and the book is not about terror. 

```{r}
library(dplyr)
library(magrittr)
```


```{r}
l1<-tnum.query("subj:New_Hampshire* and prop:median_household_income and numval:<50000")
mapply(FUN = tnum.addTag,
       guid = l1$id,
       tag = "county:poor1",
       text = "the poorest counties in New Hampshire")
l2<-tnum.query("subj:Maine* and prop:median_household_income and numval:<50000")
mapply(FUN = tnum.addTag,
       guid = l2$id,
       tag = "county:poor1",
       text = "the poor counties in Maine")
l3<-tnum.query("county:poor1")
df1<- data.frame(l3)
df1$tag<-rep("county:poor1",6)
df1 %<>% select(tag,subject,wrapper,value)
kable(df1)


```


